---
title: "Example RMD Document"
author: "Richard Sweeney"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    pdf_document:
    toc: no
fig_height: 3
fig_width: 6
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output") }) # saves 
#TO RENDER THIS FILE USE 
#rmarkdown::render("Example.Rmd", output_dir = "../output")
---

<style>

table, td, th {
  border: none;
  padding-left: 1em;
  padding-right: 1em;
  min-width: 50%;
  margin-left: auto;
  margin-right: auto;
  margin-top: 1em;
  margin-bottom: 1em;
}

</style>
    
## Overview
Example RMD document 

Some common features 
- knits to PDF in a specified output folder (default is where code is)
- makes nice tables (using stargazer)

Example based the that stargazer [cheatsheet](https://www.jakeruss.com/cheatsheets/stargazer/).

```{r basic_setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

out_type = "latex" # set this to html when working in Rstudio

#===========================================================================
# SETUP
#===========================================================================
root <- getwd()

library(tidyverse)
library(lubridate)
library(lfe)
library(texreg)
library(stargazer)
library(alpaca)
library(kableExtra)
library(ggplot2)

```
## Load the data 
```{r load_data, include = FALSE}

library("nycflights13")

daily <- flights %>%
  filter(origin == "EWR") %>%
  group_by(year, month, day) %>%
  summarise(delay = mean(dep_delay, na.rm = TRUE))

daily_weather <- weather %>%
  filter(origin == "EWR") %>%
  group_by(year, month, day) %>%
  summarise(temp   = mean(temp, na.rm = TRUE),
            wind   = mean(wind_speed, na.rm = TRUE),
            precip = sum(precip, na.rm = TRUE))

# Merge flights with weather data frames
both <- daily %>%
  inner_join(y = daily_weather, by = c("year", "month", "day")) %>% 
  data.frame()  # Temporary fix

# Create an indicator for quarter
both$quarter <- cut(both$month, breaks = c(0, 3, 6, 9, 12), 
                                labels = c("1", "2", "3", "4"))

# Create a vector of class logical
both$hot <- as.logical(both$temp > 85)
```

## Summarize the data 
Uses the default stargazer summary table

```{r sumstats, results='asis',warning=FALSE} 
stargazer(both, type = out_type ,header = FALSE)

ggplot(both, aes(precip, delay)) + geom_point()

```    
---
## Run some regressions 

```{r, results='asis',warning=FALSE} 

output  <- lm(delay ~ temp + wind + precip, data = both)
output2 <- lm(delay ~ temp + wind + precip + quarter, data = both)

it_type = "latex"
stargazer(output, output2, omit.stat=c("LL","ser","f"),
              omit.table.layout = c("dl"),
              add.lines = list(c("Model","Log","Pois","Log","Pois","Log","Pois","Log","Pois"),
                               c("Spec","GY20","GY20","GY10","GY10","GY5","GY5","bs6","bs6")),
              title = "Title",type=out_type,header = FALSE)
```